---
output:
  pdf_document: default
  html_document: default
---
 Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
 51, 35, 24, 33, 41

```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
         35, 31, 27, 22, 37, 34, 19, 20, 57, 49,
         50, 37, 46, 25, 17, 37, 42, 53, 41,
         51, 35, 24, 33, 41)
age
```

a. 

```{r}
length(age)
```
2.Find the reciprocal of the values for age

```{r}
reciprocal_age <- 1 / age
reciprocal_age
```

3. Assign also new_age <- c(age, 0, age)

```{r}
new_age <- c(age, 0, age)
new_age
```

4. Sort the values for age.

```{r}
sorted_age <- sort(age)
sorted_age
```

5. Find the minimum and maximum value for age


```{r}
min_age <- min(age)
min_age
```

```{r}
max_age <- max(age)
max_age
```

6.Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
 2.3, 2.5, 2.3, 2.4, and 2.7

```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
data
```

7. Generates a new vector for data where you double every value of the data. | What
 happen to the data
 -the contents of the data vector doubled in value.

```{r}
doubled_data <- data * 2
doubled_data
```

 8. Generate a sequence for the following scenario
 
 8.1 Integers from 1 to 100

```{r}
a81 <- seq (1: 100)
a81
```

8.2 Numbers from 20 to 6


```{r}
a82 <- seq (20, 60)
a82
```

8.3 Mean of numbers from 20 to 60

```{r}
a83 <- mean (20, 60)
a83
```

8.4 Sum of numbers from 51 to 9

```{r}
a84 <- sum(51:91)
a84

```

8.5 Integers from 1 to 1,000

```{r}
a85 <- seq (1: 1000)
a85
```


```{r}
b81 <- length(a81)
b81
```


```{r}
b82 <- length(a82)
b82
```


```{r}
b83 <- length(a83)
b83
```


```{r}
b84 <- length(a84)
b84
```

 a. How many data points from 8.1 to 8.4?_


```{r}
totb <- sum(b81, b82, b83, b84)
totb
```

 c. For 8.5 find only maximum data points until 10


```{r}
b85 <- max(1:10)
b85
```


9. *Print a vector with the integers between 1 and 100 that are not divisible by 3, 5 and
 7 using filter option

```{r}
filtnum <-  Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))
filtnum
```

10. Generate a sequence backwards of the integers from 1 to 100.

```{r}
back <- sort(1:100, decreasing = TRUE )
back
```

11. List all the natural numbers below 25 that are multiples of 3 or 5.

```{r}
f11 <- Filter(function(i) { i %% 3 == 0 || i %% 5 == 0 }, seq(25))
f11
```

Find the sum of these multiples

```{r}
totf11f <- sum(f11)
totf11f
```



```{r}
b10 <- length(filtnum)
b10
```

 a. How many data points from 10 to 11

```{r}
b11 <- length (f11)
b11
```

 12. Statements can be grouped together using braces ‘{’ and ‘}’. A group of statements
is sometimes called a block. Single statements are evaluated when a new line is typed
 at the end of the syntactically complete statement. Blocks are not evaluated until a
new line is entered after the closing brace.

```{r}
#x <- {0 + x + 5 + } (the code does not work because of a syntax error)#
```
 
  13. *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75,
75 and 77. To access individual elements of an atomic vector, one generally uses the
x[i] construction
 
 
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
 score[2]
 score[3]
```
 
 14. *Create a vector a = c(1,2,NA,4,NA,6,7).
 
 a.
 
```{r}
a = c(1,2,NA,4,NA,6,7)
print(a,na.print="-999")
```
 
 15. A special type of function calls can appear on the left hand side of the assignment
operator as in > class(x) <- "foo"
 
 
```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```
What is the output of the above code?
-It asks the user to input their age and name then prints it in a format.


 
