---
title: "RWorksheet_Trongoy#4c"
author: "George Eduard Trongoy"
date: "2024-11-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. 

a.
```{r}
library(ggplot2)
library(dplyr)

data(mpg)
write.csv(mpg, "mpg_data.csv", row.names = FALSE)
mpg_data <- read.csv("mpg_data.csv")
mpg_data
```
b.
 the categorical variables are: manufacturer, model, trans(type of transmisionn), drv(type of drive train), fl(type of fuel consumed), class(the type of car)
 
c.
the contiuous vaiables are: displ(the engine displacement), year(manufacturing date), cyl(number pf cylinders), city(city miles per gallon), hwy(highway miles per galon)


2.
a.
```{r}
manufacturer_model_counts <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))

# result
manufacturer_model_counts

model_variations <- mpg %>%
  group_by(model) %>%
  summarise(variations = n()) %>%
  arrange(desc(variations))

# result
model_variations
```

b. 
using basic plot:

```{r}
barplot(manufacturer_model_counts$unique_models, 
        names.arg = manufacturer_model_counts$manufacturer, 
        las = 2, col = "purple", main = "Unique Models by Manufacturer", 
        xlab = "Manufacturer", ylab = "Number of Unique Models")
```
using ggplot2:
```{r}
library(ggplot2)

ggplot(manufacturer_model_counts, aes(x = reorder(manufacturer, -unique_models), y = unique_models)) +
  geom_bar(stat = "identity", fill = "black") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Number of Unique Models by Manufacturer", x = "Manufacturer", y = "Unique Models")
```
2.
```{r}
ggplot(mpg, aes(x = model, y = manufacturer)) +
  geom_point() +
  labs(title = "Relationship between Car Model and Manufacturer",
       x = "Car Model",
       y = "Manufacturer") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

a.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
it plotted the relationship between model and manufacturer but the model axis seems to be compressed to the point of being glitchy.


b.
The plot gives a basic sense of how car models relate to their manufacturers, but it might not be super helpful as it is right now. If there are a lot of different models and manufacturers, the visualization can get pretty cluttered, making it hard to draw any meaningful insights. It may not convey much useful information at first glance.

3.
```{r}

top_20_mpg <- mpg[order(mpg$year), ][1:20, ]


ggplot(top_20_mpg, aes(x = factor(year), y = model)) +
  geom_jitter(width = 0.2, height = 0.2) +  
  labs(title = "Top 20 Car Models by Year",
       x = "Year",
       y = "Car Model") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 
```
4.
```{r}
car_counts <- mpg %>%
  group_by(model) %>%
  summarise(num_cars = n()) %>%
  arrange(desc(num_cars)) 

car_counts
```

a.
```{r}

```

