---
title: "RWorksheet_Trongoy#4c"
author: "George Eduard Trongoy"
date: "2024-11-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. 

a.
```{r}
library(ggplot2)
library(dplyr)

data(mpg)
write.csv(mpg, "mpg_data.csv", row.names = FALSE)
mpg_data <- read.csv("mpg_data.csv")
mpg_data
```
b.
 the categorical variables are: manufacturer, model, trans(type of transmisionn), drv(type of drive train), fl(type of fuel consumed), class(the type of car)
 
c.
the contiuous vaiables are: displ(the engine displacement), year(manufacturing date), cyl(number pf cylinders), city(city miles per gallon), hwy(highway miles per galon)


2.
a.
```{r}
manufacturer_model_counts <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))

# result
manufacturer_model_counts

model_variations <- mpg %>%
  group_by(model) %>%
  summarise(variations = n()) %>%
  arrange(desc(variations))

# result
model_variations
```

b. 
using basic plot:

```{r}
barplot(manufacturer_model_counts$unique_models, 
        names.arg = manufacturer_model_counts$manufacturer, 
        las = 2, col = "purple", main = "Unique Models by Manufacturer", 
        xlab = "Manufacturer", ylab = "Number of Unique Models")
```
using ggplot2:
```{r}
library(ggplot2)

ggplot(manufacturer_model_counts, aes(x = reorder(manufacturer, -unique_models), y = unique_models)) +
  geom_bar(stat = "identity", fill = "black") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Number of Unique Models by Manufacturer", x = "Manufacturer", y = "Unique Models")
```
2.
```{r}
ggplot(mpg, aes(x = model, y = manufacturer)) +
  geom_point() +
  labs(title = "Relationship between Car Model and Manufacturer",
       x = "Car Model",
       y = "Manufacturer") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

a.
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
it plotted the relationship between model and manufacturer but the model axis seems to be compressed to the point of being glitchy.


b.
The plot gives a basic sense of how car models relate to their manufacturers, but it might not be super helpful as it is right now. If there are a lot of different models and manufacturers, the visualization can get pretty cluttered, making it hard to draw any meaningful insights. It may not convey much useful information at first glance.

3.
```{r}

top_20_mpg <- mpg[order(mpg$year), ][1:20, ]


ggplot(top_20_mpg, aes(x = factor(year), y = model)) +
  geom_jitter(width = 0.2, height = 0.2) +  
  labs(title = "Top 20 Car Models by Year",
       x = "Year",
       y = "Car Model") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 
```
4.
```{r}
car_counts <- mpg %>%
  group_by(model) %>%
  summarise(num_cars = n()) %>%
  arrange(desc(num_cars)) 

car_counts
```

a.
```{r}
library(ggplot2)
library(dplyr)



mpg_top20 <- mpg %>% head(20)

model_counts <- mpg_top20 %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

ggplot(model_counts, aes(x = reorder(model, -car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  labs(title = "Car Count per Model (Top 20 Observations)",
       x = "Car Model", 
       y = "Count of Cars") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = rainbow(nrow(model_counts)))

```
b. 
```{r}
library(ggplot2)
library(dplyr)


model_counts <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

ggplot(model_counts, aes(x = reorder(model, car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flips the coordinates to make horizontal bars
  labs(title = "Number of Cars per Model", 
       x = "Car Model", 
       y = "Count of Cars") +
  theme_minimal() +
  theme(legend.position = "none") +  # Hide the legend
  scale_fill_manual(values = rainbow(nrow(model_counts)))

```
5. a. The relationship between the number of cylinders and engine displacement is generally positive, meaning that as the number of cylinders increases, the engine displacement tends to increase as well. This suggests that cars with more cylinders typically have larger engines in terms of displacement.

```{r}
library(ggplot2)


ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point(size = 3) +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement (Liters)",
       color = "Engine Displacement") +
  theme_minimal()

```
6.1. The scatter plot reveals a negative correlation between engine displacement (displ) and highway miles per gallon (hwy), indicating that as engine displacement increases, highway MPG tends to decrease. This output arises because larger engines typically consume more fuel, leading to lower fuel efficiency on the highway, reflecting the trade-off between engine size and fuel economy in vehicles.

```{r}
library(ggplot2)



ggplot(mpg, aes(x = displ, y = hwy, color = displ)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (Liters)",
       y = "Highway MPG",
       color = "Engine Displacement") +
  theme_minimal()

```
6.2. 
```{r}
traffic <- read.csv("traffic.csv")


```
a. 
```{r}

num_observations <- nrow(traffic)
print(paste("Number of observations:", num_observations))

variables <- colnames(traffic)
print("Variables in the dataset:")
print(variables)

```
b. 
```{r}


junction_subsets <- split(traffic, traffic$Junction)


```
```{r}
library(ggplot2)
library(dplyr)


traffic$DateTime <- as.POSIXct(traffic$DateTime, format="%Y-%m-%d %H:%M:%S")

ggplot(traffic, aes(x = DateTime, y = Vehicles, color = factor(Junction))) +
  geom_line() +
  labs(title = "Traffic Volume Over Time by Junction",
       x = "Date and Time",
       y = "Number of Vehicles",
       color = "Junction") +
  theme_minimal() +
  facet_wrap(~ Junction, scales = "free_y")

```
7. 
```{r}
library(readxl)

alexa <- read_xlsx("alexa.xlsx")

```

a. 
```{r}
n <- nrow(alexa)
print(paste("Number of observations:", n))

v <- colnames(alexa)
print("Variables in the dataset:")
print(variables)
```
b. 
```{r}
library(dplyr)


variation_counts <- alexa %>%
  group_by(variation) %>%
  summarise(total = n())

print(variation_counts)

```
c. The plot presents the more popular choice and what the customers preffer more.

```{r}
ggplot(variation_counts, aes(x = reorder(variation, -total), y = total, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Count of Each Product Variation",
       x = "Product Variation",
       y = "Total Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```
d. 
```{r}
alexa$date <- as.Date(alexa$date)

daily_reviews <- alexa %>%
  group_by(date) %>%
  summarise(total_verified_reviews = sum(feedback))

ggplot(daily_reviews, aes(x = date, y = total_verified_reviews)) +
  geom_line(color = "blue") +
  labs(title = "Number of Verified Reviews Over Time",
       x = "Date",
       y = "Total Verified Reviews") +
  theme_minimal()
```
e. 
```{r}
library(dplyr)
library(ggplot2)

variation_ratings <- alexa %>%
  group_by(variation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%

arrange(desc(average_rating))

variation_ratings
```


```{r}
hv <- variation_ratings %>%
  slice(1)
hv
```


```{r}
ggplot(variation_ratings, aes(x = reorder(variation, -average_rating), y = average_rating, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Rating by Product Variation",
       x = "Product Variation",
       y = "Average Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```
